\section{Manifesto: A Vision for Safe Autonomous Prediction Market Trading}\label{sec:manifesto}

Prediction markets are not merely financial instruments. They are information markets, belief-aggregation mechanisms, and decision-support tools for the most consequential questions of our time: climate change, geopolitical stability, technological progress, and democratic governance. As Artificial General Intelligence (AGI) enters these markets, the stakes transcend individual profit. An autonomous AI that can trade prediction markets is an AI that can shape collective beliefs. This power demands responsibility.

We believe that the future of autonomous trading is not a race to maximum returns. It is a race to maximum safety. The system that trades the most aggressively is not the winner; the system that trades the most responsibly is.

\subsection{Safety as a Competitive Advantage}

We reject the false dichotomy between performance and safety. In prediction markets, long-term profitability depends on calibration, not bravado. A system that respects its risk boundaries, that pauses when data is stale, that retires strategies before they erode capital---such a system will outlast flashier competitors. Darwinian selection applies not to the most profitable strategy, but to the most durable. PolyEdge's bounded autonomy framework, health-based kill checks, and hard LLM budget caps are not constraints on performance. They are competitive advantages in the marathon of financial Darwinism.

\subsection{Open-Source Collaborative Intelligence}

We believe that autonomous trading systems should be open-source. Not because open-source is inherently safer, but because safety requires scrutiny. The StrategyGenome model, with its modular chromosomes and auditable lineage, enables community oversight of how strategies evolve. The dual-debate ledger provides public evidence of how decisions were justified. The promotion pipeline exposes every experiment to automated validation before it touches live capital. These mechanisms are designed to withstand inspection.

We invite researchers, developers, and market participants to fork the codebase, challenge our assumptions, and propose improvements. The genome repository is a public commons: every strategy that fails is a lesson shared; every strategy that succeeds is a template for others. We do not claim to have solved autonomous trading; we claim to have built a platform for solving it together.

\subsection{The Role of Prediction Markets in an AGI World}

Prediction markets have a unique role in the era of AGI. They are one of the few arenas where AI systems can compete in a zero-sum, high-stakes environment with verifiable outcomes. The accuracy of prediction market prices is a signal of collective intelligence---human and artificial combined. An autonomous trading system that improves market calibration, that reduces noise, that identifies and corrects mispricings, is not extracting wealth from the market. It is contributing to the market.

We envision a future in which autonomous prediction market agents are not adversaries but collaborators: sharing anonymized strategies, cross-validating each other's predictions, and collectively improving the accuracy of forecasts that matter to humanity. This vision requires trust, and trust requires safety. Bounded autonomy is the foundation.

\subsection{Our Commitment}

We commit to the following principles:
\begin{enumerate}
    \item \textbf{Honesty over Hype.} We will report our results honestly, including negative returns, failed experiments, and design flaws. Publish-ready means truth-ready.
    \item \textbf{Safety over Speed.} We will not bypass safety gates for short-term performance gains. No configuration flag will override risk profiles without explicit human opt-in.
    \item \textbf{Openness over Secrecy.} We will open-source our code, data, and experimental protocols. We will not hide behind proprietary algorithms.
    \item \textbf{Evolution over Revolution.} We will improve incrementally, through mutation, crossover, and fitness selection. We will not bet the farm on unproven strategies.
    \item \textbf{Community over Competition.} We will share our failures so others can learn. We will celebrate their successes as our own.
\end{enumerate}

The PolyEdge system, with its 162 trades, 25 experiments, and $-$622 USDC P\&L, is not a finished product. It is a beginning. We invite you to join us in building a future where autonomous AI and prediction markets serve not only profit, but truth.
